Plot Intercoder Agreement

### 2022-03-24 replication_data/rmd/02_format_and_clean.rmd
condition location update

#Locations and dates are both really hard to do
dictionary_locations <- readxl::read_excel(target_file, sheet="locations", na = c("", "NA")) 
dictionary_dates <- readxl::read_excel(target_file, sheet="dates", col_types="text") #This is the tricky one and why he had to add values

@@

@@

```{r}
 #LOCATION
icb_long_location_clean <- icb_long_split %>% 
  dplyr::filter(variable == "interact_location_other") %>% 
  dplyr::full_join(location_merge_directory %>%
                     dplyr::mutate(crisno = as.character(crisno)) %>% 
                     dplyr::rename(value = interact_location_other)) %>% 
  dplyr::rename(value_normalized = norm_name) %>%
  dplyr::mutate(variable_normalized = "interact_location_other_clean") %>%   
  dplyr::select(-do_actor_a, -do_actor_b, -interact_location) %>% 
  dplyr::mutate(value_normalized = ifelse(is.na(value_normalized), "no_cleaning", value_normalized))
```

@@

icb_long_clean <- icb_long_split %>% 
  dplyr::left_join(icb_long_action_clean, by=names(icb_long_split)) %>% 
  dplyr::left_join(icb_long_actor_clean, by=names(icb_long_split), suffix = c("", ".actor")) %>% 
      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable_normalized.actor, variable_normalized))) %>%
      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value_normalized.actor, value_normalized))) %>%
      dplyr::select(-variable_normalized.actor, -value_normalized.actor) %>% 
  dplyr::left_join(icb_long_location_clean, by=names(icb_long_split), suffix = c("", ".location")) %>% 
      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable_normalized.location, variable_normalized))) %>%
      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value_normalized.location, value_normalized))) %>%
      dplyr::select(-variable_normalized.location, -value_normalized.location) %>% 
  dplyr::full_join(icb_long_dates_clean, by=names(icb_long_split), suffix = c("", ".date")) %>% 
      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable_normalized.date, variable_normalized))) %>%
      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value_normalized.date, value_normalized))) %>%
      dplyr::select(-variable_normalized.date, -value_normalized.date)

@@

```{r}
# Fix several typos:

@@

icb_long_clean2 <- icb_long_clean %>% 
                            dplyr::distinct() %>%
                            dplyr::mutate(variable_normalized= variable_normalized %>%
                                            stringr::str_replace("_other_clean","")) %>% 
  #We want to collapse others in with regulars
                            dplyr::mutate(variable_normalized= variable_normalized %>% 
                                            stringr::str_replace("_clean","")) %>% 
  #These only exist with actors now
                            dplyr::mutate(variable_normalized= variable_normalized %>% 
                                            stringr::str_replace("_other","")) %>% 
  #Only really matters for location_other

                            dplyr::filter(value_normalized!='drop') %>%
                            dplyr::filter(email_id!='expert3') %>% #expert3 Looks broken all the time
                            #I'm going to move to a structure where event numbers can have a subsection that is condition rather than keeping it in the variable names
                            dplyr::mutate(event_number_int_condition=variable_normalized %>%
                                            stringr::str_detect('condition_') %>% as.numeric() ) %>%
                            dplyr::mutate(variable_normalized=variable_normalized %>%
                                            stringr::str_replace('condition_',''))

# THIS IS WHERE I AM
# give every entry its own event_type var to control merging (avoid merging in details for actions that were 'thought about' or 'said')
# confirm that no email_crisis_sent_event have more than one event_type entry
icb_long_clean2 %>% dplyr::filter(variable_normalized == "event_type") %>% 
  dplyr::select("email_crisis_sent_event", "value_normalized") %>% 
  dplyr::rename(event_type=value_normalized) %>% dplyr::count(email_crisis_sent_event) %>% dplyr::filter(n>1)

@@

>>>>

#Locations and dates are both really hard to do
dictionary_locations <- readxl::read_excel(target_file, sheet="locations", na = c("", "NA")) 
dictionary_condition_locations <- readxl::read_excel(target_file, sheet="condition_locations", na = c("", "NA")) 
dictionary_dates <- readxl::read_excel(target_file, sheet="dates", col_types="text") #This is the tricky one and why he had to add values

@@

condition_location_merge_directory <- icb_wide_aligned %>% 
    dplyr::mutate(crisno3 = stringr::str_pad(crisno, 3, pad = "0"), 
                  sentence_number_int_aligned3 = stringr::str_pad(sentence_number_int_aligned, 3, pad = "0")) %>% 
  dplyr::mutate(email_crisis_sent_event = paste(email_id,crisno3,sentence_number_int_aligned3,event_number_int, sep="_")) %>%
  dplyr::select(-crisno3, -sentence_number_int_aligned3) %>%
  dplyr::mutate(crisis_sent = paste0(crisno,"_",sentence_number_int_aligned)) %>%
  dplyr::select(crisno, email_crisis_sent_event, do_actor_a, do_actor_b, condition_interact_location, condition_interact_location_other) %>% 
  dplyr::mutate(do_actor_a=strsplit(do_actor_a, ";")) %>% tidyr::unnest(do_actor_a) %>%
  dplyr::mutate(do_actor_b=strsplit(do_actor_b, ";")) %>% tidyr::unnest(do_actor_b) %>%
  dplyr::mutate(condition_interact_location_other=strsplit(condition_interact_location_other, ";")) %>% tidyr::unnest(condition_interact_location_other) %>%
  dplyr::mutate(do_actor_a=tolower(do_actor_a), do_actor_b=tolower(do_actor_b),
                condition_interact_location_other=trimws(tolower(condition_interact_location_other))) %>%
  dplyr::left_join(dictionary_condition_locations %>%
                     dplyr::mutate() %>% 
                     dplyr::mutate(condition_interact_location_other = tolower(condition_interact_location_other)) %>% 
                     dplyr::select(do_actor_a, do_actor_b, condition_interact_location, condition_interact_location_other, norm_name)) %>%
  dplyr::mutate(crisno = as.numeric(crisno)) %>% 
  unique() %>% 
  dplyr::filter(!is.na(condition_interact_location_other))

@@

```{r}
 #LOCATION
icb_long_location_clean <- icb_long_split %>% 
  dplyr::filter(variable == "interact_location_other") %>% 
  dplyr::full_join(location_merge_directory %>%
                     dplyr::mutate(crisno = as.character(crisno)) %>% 
                     dplyr::rename(value = interact_location_other)) %>% 
  dplyr::rename(value_normalized = norm_name) %>%
  dplyr::mutate(variable_normalized = "interact_location_other_clean") %>%   
  dplyr::select(-do_actor_a, -do_actor_b, -interact_location) %>% 
  dplyr::mutate(value_normalized = ifelse(is.na(value_normalized), "no_cleaning", value_normalized))

icb_long_condition_location_clean <- icb_long_split %>% 
  dplyr::filter(variable == "condition_interact_location_other") %>% 
  dplyr::full_join(condition_location_merge_directory %>%
                     dplyr::mutate(crisno = as.character(crisno)) %>% 
                     dplyr::rename(value = condition_interact_location_other)) %>% 
  dplyr::rename(value_normalized = norm_name) %>%
  dplyr::mutate(variable_normalized = "condition_interact_location_other_clean") %>%   
  dplyr::select(-do_actor_a, -do_actor_b, -condition_interact_location) %>% 
  dplyr::mutate(value_normalized = ifelse(is.na(value_normalized), "no_cleaning", value_normalized))

@@

icb_long_clean <- icb_long_split %>% 
  dplyr::left_join(icb_long_action_clean, by=names(icb_long_split)) %>% 
  dplyr::left_join(icb_long_actor_clean, by=names(icb_long_split), suffix = c("", ".actor")) %>% 
      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable_normalized.actor, variable_normalized))) %>%
      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value_normalized.actor, value_normalized))) %>%
      dplyr::select(-variable_normalized.actor, -value_normalized.actor) %>% 
  dplyr::left_join(icb_long_location_clean, by=names(icb_long_split), suffix = c("", ".location")) %>% 
      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable_normalized.location, variable_normalized))) %>%
      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value_normalized.location, value_normalized))) %>%
      dplyr::select(-variable_normalized.location, -value_normalized.location) %>% 
  dplyr::left_join(icb_long_condition_location_clean, by=names(icb_long_split), suffix = c("", ".condition_location")) %>% 
      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable_normalized.condition_location, variable_normalized))) %>%
      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value_normalized.condition_location, value_normalized))) %>%
      dplyr::select(-variable_normalized.condition_location, -value_normalized.condition_location) %>% 
  dplyr::full_join(icb_long_dates_clean, by=names(icb_long_split), suffix = c("", ".date")) %>% 
      dplyr::mutate(variable_normalized = (ifelse(is.na(variable_normalized), variable_normalized.date, variable_normalized))) %>%
      dplyr::mutate(value_normalized = (ifelse(is.na(value_normalized), value_normalized.date, value_normalized))) %>%
      dplyr::select(-variable_normalized.date, -value_normalized.date)

@@

```{r}
# Fix typos:

@@

```{r}
icb_long_clean2 <- icb_long_clean %>% 
  dplyr::distinct() %>%
  dplyr::mutate(variable_normalized= variable_normalized %>%
                  stringr::str_replace("interact_location_other_clean","interact_location_defined")) %>%
  dplyr::mutate(variable_normalized= variable_normalized %>%
                  stringr::str_replace("condition_interact_location_other","condition_interact_location_defined")) %>% 
  dplyr::mutate(variable_normalized= variable_normalized %>%
                  stringr::str_replace("_other_clean","")) %>% 
  #We want to collapse others in with regulars
  dplyr::mutate(variable_normalized= variable_normalized %>% 
                  stringr::str_replace("_clean","")) %>% 
  #These only exist with actors now
  dplyr::mutate(variable_normalized= variable_normalized %>% 
                  stringr::str_replace("_other","")) %>% 
  #Only really matters for location_other
  dplyr::filter(value_normalized!='drop') %>%
  dplyr::filter(email_id!='expert3') %>% #expert3 Looks broken all the time
  #I'm going to move to a structure where event numbers can have a subsection that is condition rather than keeping it in the variable names
  dplyr::mutate(event_number_int_condition=variable_normalized %>%
                  stringr::str_detect('condition_') %>% as.numeric() ) %>%
  dplyr::mutate(variable_normalized=variable_normalized %>%
                  stringr::str_replace('condition_',''))

# give every entry its own event_type var to control merging (avoid merging in details for actions that were 'thought about' or 'said')
# confirm that no email_crisis_sent_event have more than one event_type entry
icb_long_clean2 %>% dplyr::filter(variable_normalized == "event_type") %>% 
  dplyr::select("email_crisis_sent_event", "value_normalized") %>% 
  dplyr::rename(event_type=value_normalized) %>% dplyr::count(email_crisis_sent_event) %>% dplyr::filter(n>1)

@@

# icb_long_clean %>% dplyr::select(variable_normalized) %>% table()
# 
# icb_long_clean %>% dplyr::filter(variable_normalized=="interact_location") %>% dplyr::select(value_normalized) %>% table()
# icb_long_clean %>% dplyr::filter(variable_normalized=="condition_interact_location_other") %>% dplyr::select(value_normalized) %>% table()
# 
# icb_long_clean2 %>% dplyr::filter(variable_normalized=="interact_location") %>% dplyr::select(value_normalized) %>% table()
# icb_long_clean2 %>% dplyr::filter(variable_normalized=="interact_location_defined") %>% dplyr::select(value_normalized) %>% table()
# 
# temp <- icb_wide_aligned_raw %>% dplyr::select("do_actor_a", "do_actor_b", "condition_interact_location", "condition_interact_location_other") %>% dplyr::filter(!is.na(condition_interact_location_other))

### 2022-03-24 replication_data/rmd/03_aggregation.Rmd
condition location update

 if(exists("temp_long")){
   temp_long <- dplyr::bind_rows(temp_long, temp_long_partial)
   }else{
     temp_long <- temp_long_partial
   }
}
```

@@

#
#
#
#Maybe we use this as a screen on the original codings and then collect what survived to make subevents?
rex_paste <- function(x){ paste0(x %>% unlist() %>% trimws() %>% sort() %>% unique() %>% na.omit(), collapse=";")  }
codings_wide_agreed <- icb_long_clean  %>% arrange(crisno,sentence_number_int_aligned) %>%
                        #filter(crisno==59) %>%
                        inner_join(codings_long_agreed) %>% #only keep ones that show up in both
                        filter(email_id %>% str_detect('expert') ) %>%
                        dplyr::select(email_id,crisno,sentence_number_int_aligned, event_number_int, event_number_int_condition, sentence,variable_normalized, value_normalized) %>%
                        distinct() %>%
                        pivot_wider(id_cols=c(email_id,crisno,sentence_number_int_aligned, sentence,event_number_int, event_number_int_condition), 
                                    names_from=variable_normalized, values_from=value_normalized, values_fn=rex_paste) %>%
                        distinct() %>%
                        group_by(crisno,sentence_number_int_aligned, event_number_int_condition, sentence, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>%
                          dplyr::summarise_all(rex_paste)
                        #filter(crisno==59 & sentence_number_int_aligned==3) 
codings_wide_agreed[codings_wide_agreed == ""]<-NA
#do the filters here after guaranteeing NAs

>>>>

 if(exists("temp_long")){
   temp_long <- dplyr::bind_rows(temp_long, temp_long_partial)
   }else{
     temp_long <- temp_long_partial
   }

  # for debugging
    # try(if("icb_survey_version" %in% names(temp_long$icb_survey_version)) stop("icb_survey_version appeared..."))

}
```

@@

#
#
#
#Maybe we use this as a screen on the original codings and then collect what survived to make subevents?
rex_paste <- function(x){ paste0(x %>% unlist() %>% trimws() %>% sort() %>% unique() %>% na.omit(), collapse=";")  }
codings_wide_agreed <- icb_long_clean  %>% arrange(crisno,sentence_number_int_aligned) %>%
                        #filter(crisno==59) %>%
                        dplyr::inner_join(codings_long_agreed) %>% #only keep ones that show up in both
                        filter(email_id %>% str_detect('expert') ) %>%
                        dplyr::select(email_id,crisno,sentence_number_int_aligned, event_number_int, event_number_int_condition, sentence,variable_normalized, value_normalized) %>%
                        distinct() %>%
                        pivot_wider(id_cols=c(email_id,crisno,sentence_number_int_aligned, sentence,event_number_int, event_number_int_condition), 
                                    names_from=variable_normalized, values_from=value_normalized, values_fn=rex_paste) %>%
                        distinct() %>%
                        group_by(crisno,sentence_number_int_aligned, event_number_int_condition, sentence, say_actor_a, say_actor_b, do_actor_a, do_actor_b) %>%
                          dplyr::summarise_all(rex_paste)
                        #filter(crisno==59 & sentence_number_int_aligned==3) 
codings_wide_agreed[codings_wide_agreed == ""]<-NA
#do the filters here after guaranteeing NAs

### 2022-03-24 replication_paper/rmd/05_ICBEdataset_paper_PlotInterCoderAgreement.Rmd
plot reorder
condition location update

```{r}

@@

#These are all by definition chosen by at least 1
#Do we further require at least 1 expert as with our aggregations?
p_percent_chose_tag_by_concept <- 
  codings_long_agreement %>% #codings_long %>%  codings_long_agreement
    mutate(variable_normalized=variable_normalized %>% str_replace_all("_"," ") %>% tolower() ) %>%
    filter(value_normalized!='') %>%
    filter(total_coders>1) %>% #about 9k only had one coder
    #filter(selected_by_experts>=1) %>%
    dplyr::select(variable_normalized,selected_by_any_perc,selected_by_experts_perc,selected_by_undergrads_perc,keep) %>%
    group_by(variable_normalized) %>%
      summarise(
          N=n(),
          Accepted=selected_by_any_perc[keep==1] %>% mean(na.rm=T), 
          All=selected_by_any_perc %>% mean(na.rm=T), 
          Experts=selected_by_experts_perc %>% mean(na.rm=T), 
          Undergraduates=selected_by_undergrads_perc %>% mean(na.rm=T)
      ) %>%
    filter(N>10) %>%
    dplyr::select(-N) %>%
    mutate(variable_normalized=fct_reorder(variable_normalized, Accepted)) %>%
    pivot_longer(c(-variable_normalized)) %>%
    ggplot(aes(x=selected_by_any_perc, y=variable_normalized)) + 
    #geom_boxplot() + 
    geom_point(aes(x=value, color=name )) +
    xlab("Percent of Coders that selected Tag") +
    ylab("") +
    labs(
      # title = "Intercoder Agreement by Concept/Type",
      # subtitle = "Mean by Concept (points), Mean by Group (Vertical Lines)",
          caption = paste0("Point = mean by concept; Line = mean by group\nUnit of Analysis: Tag chosen by any Coder, N=", codings_long_agreement %>% filter(value_normalized!='') %>% nrow() %>% scales::comma(), "; Accepted Tokens=", codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() %>% scales::comma()),
         color = "Codings"
         ) + 
    theme_bw() +
    theme(legend.position="bottom") +
    geom_vline(data=meansall, aes(xintercept = value, color = name), linetype="solid", size=1, alpha=0.5)

>>>>

```{r}
#codings_long_agreement <- codings_long_agreement %>% dplyr::filter(event_number_int_condition == 0)

@@

#These are all by definition chosen by at least 1
#Do we further require at least 1 expert as with our aggregations?
p_percent_chose_tag_by_concept <- 
  codings_long_agreement %>% #codings_long %>%  codings_long_agreement
    mutate(variable_normalized=variable_normalized %>% str_replace_all("_"," ") %>% tolower() ) %>%
    filter(value_normalized!='') %>%
    filter(total_coders>1) %>% #about 9k only had one coder
  # filter(event_number_int_condition==0) %>%
    #filter(selected_by_experts>=1) %>%
    dplyr::select(variable_normalized,selected_by_any_perc,selected_by_experts_perc,selected_by_undergrads_perc,keep) %>%
    group_by(variable_normalized) %>%
      summarise(
          N=n(),
          Accepted=selected_by_any_perc[keep==1] %>% mean(na.rm=T), 
          All=selected_by_any_perc %>% mean(na.rm=T), 
          Experts=selected_by_experts_perc %>% mean(na.rm=T), 
          Undergraduates=selected_by_undergrads_perc %>% mean(na.rm=T)
      ) %>%
    filter(N>10) %>%
    dplyr::select(-N) %>%
    mutate(variable_normalized=fct_reorder(variable_normalized, Accepted)) %>%
    pivot_longer(c(-variable_normalized)) %>%
    ggplot(aes(x=selected_by_any_perc, y=variable_normalized)) + 
    #geom_boxplot() + 
    geom_point(aes(x=value, color=name )) +
    xlab("Percent of Coders that selected Tag") +
    ylab("") +
    labs(
      # title = "Intercoder Agreement by Concept/Type",
      # subtitle = "Mean by Concept (points), Mean by Group (Vertical Lines)",
          caption = paste0("Point = mean by concept; Line = mean by group\nUnit of Analysis: Tag chosen by any Coder, N=", codings_long_agreement %>% filter(value_normalized!='') %>% nrow() %>% scales::comma(), "; Accepted Tokens=", codings_long_agreement %>% filter(value_normalized!='' & keep==T) %>% nrow() %>% scales::comma()),
         color = "Codings"
         ) + 
    theme_bw() +
    theme(legend.position="bottom") +
    geom_vline(data=meansall, aes(xintercept = value, color = name), linetype="solid", size=1, alpha=0.5)
